DSSynth: An Automated Digital Controller Synthesis Tool for Physical Plants

### 2017-08-23 ase2017/paper.tex
added robust control toolbox

There are existing toolboxes for MATLAB that provide functions and scripts
to support the design and implementation of digital
controllers~\cite{matlab-toolbox}.  In~particular, there is a MATLAB Toolbox
named \emph{DSVerifier}~\cite{issta2017, DBLP:journals/tc/BessaIPCF17,
DBLP:journals/dafes/BessaICF16}, which automatically detects specific errors
in a given digital system design (e.g., errors related to stability, limit
cycle and overflow) using symbolic model checking based on Boolean
Satisfiability (SAT) and Satisfiability Modulo Theories (SMT) solvers.  The
Pessoa~\cite{mazo2010pessoa} toolbox performs synthesis of correct-by-design
digital controllers.  Pessoa is based on approximate bisimulation, which
allows control engineers to replace the differential equations (describing the
physical plant) by a finite-state machine.  However, Pessoa does
not take advantage of recent advances in bit-accurate verification of
programs to synthesize controllers w.r.t.~FWL effects.  MATLAB offers a tool
named \emph{Control System Tuner}~\cite{autotuner} for automatically
designing controllers based on optimization or graphical analysis.  However,
the Control System Tuner is unable to consider FWL effects during controller
synthesis.  To the best of our knowledge, there is no MATLAB toolbox able to
perform digital controller synthesis that considers the complete range of
approximations, including time discretization, quantization effects, and
finite-precision arithmetic and its rounding errors.

>>>>

There are existing toolboxes for MATLAB that provide functions and scripts
to support the design and implementation of digital
controllers~\cite{matlab-toolbox}.  In~particular, there is a MATLAB Toolbox
named \emph{DSVerifier}~\cite{issta2017, DBLP:journals/tc/BessaIPCF17,
DBLP:journals/dafes/BessaICF16}, which automatically detects specific errors
in a given digital system design (e.g., errors related to stability, limit
cycle and overflow) using symbolic model checking based on Boolean
Satisfiability (SAT) and Satisfiability Modulo Theories (SMT) solvers.  The
Pessoa~\cite{mazo2010pessoa} toolbox performs synthesis of correct-by-design
digital controllers.  Pessoa is based on approximate bisimulation, which
allows control engineers to replace the differential equations (describing the
physical plant) by a finite-state machine.  However, Pessoa does
not take advantage of recent advances in bit-accurate verification of
programs to synthesize controllers w.r.t.~FWL effects.  MATLAB offers a tool
named \emph{Control System Tuner}~\cite{autotuner} for automatically
designing controllers based on optimization or graphical analysis.  However,
the Control System Tuner is unable to consider FWL effects during controller
synthesis. In addition, there is another toolbox called 
\emph{Robust Control Toolbox}~\cite{robusttool}, which computes a  
stabilizing $H_{2}$ optimal controller $K$ for a partitioned LTI plant $P$. 
The main output provided by this toolbox is the controller synthesized, and also,
the closed-loop system that combines the plant and the controller synthesized. 
However, the FWL effects is not taking account as well.
To the best of our knowledge, there is no MATLAB toolbox able to
perform digital controller synthesis that considers the complete range of
approximations, including time discretization, quantization effects, and
finite-precision arithmetic and its rounding errors.
